PK object batch mode trial

### 2023-08-11 data-raw/batchMode_trial_gpm.Rmd
Bug fix for fold error function and downstream summary function

>>>>

```{r questions}
my_pk <- readRDS("data-raw/all_cvt_pk.rds")

pk_summary <- summary(my_pk)

# Q: What do "bad" fits have in common?
gof_df <- pk_summary$goodness_of_fit %>%
  inner_join(suppressMessages(get_winning_model(my_pk))) %>%
  filter(method == "L-BFGS-B") %>%
  ungroup()

## Find the within_2fold for each data_group
gof_df %>%
  dplyr::select(Chemical, Species, full_fold_errors) %>%
  unnest(full_fold_errors) %>%
  group_by(Chemical, Species) %>%
  summarize(within_2fold = sum(
    Fold_Error >= 0.5 & Fold_Error <= 2, na.rm = TRUE
    ) / length(na.omit(Fold_Error))) %>%
  filter(within_2fold == 0) %>% pull(Chemical) %>% unique()
  arrange(within_2fold) %>%
  View()

gof_df %>%
  ggplot(aes(
    x = log2(avg_FoldErr),
    y = log10(avg_rmse))) +
  geom_point() +
  geom_vline(color = "red3", xintercept = c(-1, 1))

fe_df <- fold_errors(my_pk)
# Something wrong with the summary method... maybe only use detects?
fold_errors_all <- fe_df %>%
  inner_join(suppressMessages(get_winning_model(my_pk))) %>%
  dplyr::filter(Detect %in% TRUE) %>%
  dplyr::group_by(!!!my_pk$data_group, model, method, Route, Media, Dose) %>%
  dplyr::mutate(avg_FoldErr = mean(Fold_Error, na.rm = TRUE),
                median_FoldErr = median(Fold_Error, na.rm = TRUE),
                within_2fold = sum(Fold_Error >= 0.5 & Fold_Error <= 2)/length(Fold_Error)) %>%
  dplyr::select(Time, Fold_Error,
                avg_FoldErr, median_FoldErr, within_2fold) %>%
  tidyr::nest(full_fold_errors = c(Time, Fold_Error))

fold_errors_all %>% 
  ggplot(aes(x = within_2fold)) +
  geom_histogram(binwidth = 0.1) +
  facet_grid(cols = vars(model))

fe_df %>%
  inner_join(suppressMessages(get_winning_model(my_pk))) %>%
  dplyr::filter(Detect %in% TRUE) %>%
  ggplot(aes(x = log2(Fold_Error))) +
  xlim(-4, 4) +
  geom_histogram(binwidth = 0.1) +
  facet_grid(cols = vars(model))

# Q: What do "great" fits have in common?

# Q: Does the dataset have a bias?
```
